\documentclass[11pt]{amsart}
\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   % ... or a4paper or a5paper or ... 
%\geometry{landscape}                % Activate for for rotated page geometry
%\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{epstopdf}
\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}

\title{ACM SIGHPC Education Chapter Annual Education Award Nomination Form}

%\date{}                                           % Activate to display a given date or no date

\begin{document}
\maketitle
%\section{}
%\subsection{}

\noindent
Nominator Name:  
\newline Nominator E-Mail:
\newline
\begin{bf} Project or Program Information \end{bf}
\newline
Title: \newline
Nominee Name: \newline
Nominee E-Mail: \newline

Please fill out the information below and include any additional information solicited in the form if applicable.  The final nomination packet should be submitted as a single PDF document sent to award@sighpceducation.acm.org by the application deadline. 
\newline

Awards will be judged based on the criteria set forth in the questions below.  Provide a summary statement related to each of the criteria relevant to the project or program being nominated in the form below.  Ancillary materials in support of the statements can be included as attachments to the nomination within the limits indicated in each case.  If the criterion is not applicable to this program or project please enter N/A in that section.
\newline

\noindent \begin{bf}Brief description (maximum 500 words) \end{bf}
\vskip 2.5 in










Up to three letters of endorsement by those familiar with or clients of the project/program for this nomination should be attached to the nomination packet.
\newline

\noindent  \begin{bf}Please document these aspects of the nomination as appropriate: \end{bf}
\newline
\vskip .25 in 
\noindent How does the work provide innovative training and education materials for computational science, data-enabled, or HPC education?

\vskip 1 in
\noindent Describe any available metrics of the impacts of the project/program success


\noindent How has the program enhanced the ability to engage, serve, and retain a diverse community of participants?
\vskip 1 in

\noindent Describe the extent to which the  work has received widespread adoption of their approach and/or materials by and/or participation other groups/organizations.
\vskip 1 in

\noindent Presentations and Publications associated with the program
\begin{em} Provide a list of project presentations and publications if any \end{em}



\end{document}  
